mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-10 Draft3.Rmd
add table

mathout <- function(...)
{
  if(knitr::is_html_output())
    return(mathml(...))

  if(knitr::is_latex_output())
    return(mathjax(...))

  warning("no output specified")  
  mathjax(...)
}

@@

```{r, results='asis'}
term <- quote(`%+-%`(mean(X), 1.96 * s / sqrt(N)))
term <- quote(mean(X) %+-% {1.96 * s / sqrt(N)})
mathout(term)
```

_The following can be inserted in a table_

catmath(x*y)

catmath(x %*% y)

catmath(x %.% y)

catmath(X %x% Y)

catmath(x/y)

catmath(x %/% y)
```

>>>>

mathout <- function(..., flags=NULL)
{
  if(knitr::is_html_output())
    return(mathml(..., flags=c(flags, list(cat=TRUE))))

  if(knitr::is_latex_output())
    return(mathjax(..., flags=c(flags, list(cat=TRUE))))

  warning("no output specified")  
  mathjax(..., flags=c(flags, list(cat=TRUE)))
}

@@

```{r, results='asis'}
term <- quote(`%+-%`(mean(X), 1.96 * s / sqrt(N)))
term <- quote(mean(X) %+-% {1.96 * s / sqrt(N)})   # the same
mathout(term)
```

A few more custom operators are shown in Table\ 1.

```{r, echo=FALSE}
op <- list(cross=quote(x %*% y), dot=quote(x %.% y), kronecker=quote(X %x% Y),
  'integer division'=quote(x %/% y))
m <- lapply(op, FUN=mathout, flags=list(cat=FALSE))

t <- cbind(Operator=as.character(op), Output=m)
knitr::kable(t, caption = "Custom operators in \\pkg{mathml}", 
             label="tab:custom")
```
